Timeseries Example

### 2015-12-06 README.Rmd

This is code for an ABM of a climate prediction market
in which traders adapt their belief about the climate based
on the monetary performance of their neighboring traders in
a social network. The ABM is meant to test whether climate
prediction markets foster the convergence of people’s beliefs
about the climate. The model will be used to
assess whether such convergence is impacted by factors such
as the initial belief-homophily in the social network or the
time horizon at which climate securities are realized.

[Martin Van der Linden](https://martinvdlinden.wordpress.com/) (Dept. of Economics, Vanderbilt University) and [John Nay](https://johnnay.github.io) (School of Engineering, Vanderbilt University).

Master is the main script that sources everything else.
```{r, eval=FALSE, include=TRUE}
source("master.R")
````

>>>>

This is code for an agent-based model (ABM) of a climate prediction market in which traders adapt their belief about the climate based on the monetary performance of their neighboring traders in a social network. The ABM is meant to test whether climate prediction markets foster the convergence of people’s beliefs about the climate.

[John J. Nay](http://johnjnay.com/) (School of Engineering, Vanderbilt University), [Martin Van der Linden](https://martinvdlinden.wordpress.com/) (Economics, Vanderbilt University), and [Jonathan M. Gilligan](https://my.vanderbilt.edu/jonathangilligan/) (Earth and Environmental Sciences, Vanderbilt University).
